\textbf{Empirical Bayes shrinkage, and denoising of Poisson and heteroskedastic Gaussian signals (?)}

### 2016-01-08 paper/draft_5.tex
added ash profiling

The first problem relates to mean and variance estimation with Gaussian noise. Although the framework for homoskedastic Gaussian errors has been thoroughly developed in the wavelet literature [references], methods dealing with heteroskedastic errors are uncommon. Fan \& Yao (1998) estimated the variance by smoothing the squared residuals using local polynomial smoothing, while Brown \& Levine (2007) employed difference-based kernel estimators. Making use of the local adaptivity of wavelet methods, Cai \& Wang (2008) improved upon previous variance estimation methods using a wavelet thresholding approach on first order differences. Here we present an approach that estimates both the mean and variance accurately by incorporating ASH into a novel wavelet denoising framework. [mention the lack of available software?]

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_1.pdf}
        \caption{}
        \label{fig:simple_eg_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_2.pdf}
        \caption{}
        \label{fig:simple_eg_2}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_3.pdf}
        \caption{}
        \label{fig:simple_eg_3}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_4.pdf}
        \caption{}
        \label{fig:simple_eg_4}
    \end{subfigure}
				\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_5.pdf}
        \caption{}
        \label{fig:simple_eg_5}
    \end{subfigure}
    \caption{shows both ASH and SMASH at work. (a) shows the mean and variance functions, as well as one realized dataset. (b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse and one fine. (c) demonstrates the shrinkage properties of ASH for the two scales of interest: the coefficients at the fine scale are substantially shrunk, but barely so for the coarse scale. (d) shows the shrinkage effect of ASH on the fine scale wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision. (e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has notable artifacts.}
    \label{fig:simple_eg}
\end{figure}

>>>>

Methods for smoothing the variance of Gaussian data, or even for smoothing the mean in the presence of heteroskedastic errors, 
are uncommon, particularly compared with the well-studied homoskedastic case. 
Previous non-wavelet-based work includes Fan \& Yao (1998), who estimated the variance by smoothing the squared residuals using local polynomial smoothing, and Brown \& Levine (2007) who employed difference-based kernel estimators. The only wavelet-based method we have found is Cai \& Wang (2008), which applied
a wavelet thresholding approach to first order differences. Unfortunately none of these methods have available software implementations.
mention Wand work.

@@

\begin{figure}
\centering
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_1.pdf}
        \caption{}
        \label{fig:simple_eg_1}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_2.pdf}
        \caption{}
        \label{fig:simple_eg_2}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_3.pdf}
        \caption{}
        \label{fig:simple_eg_3}
    \end{subfigure}
		\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_4.pdf}
        \caption{}
        \label{fig:simple_eg_4}
    \end{subfigure}
				\hfill
    \begin{subfigure}[b]{0.48\textwidth}
        \centering
        \includegraphics[width=\textwidth]{simple_eg_5.pdf}
        \caption{}
        \label{fig:simple_eg_5}
    \end{subfigure}
    \caption{shows both ASH and SMASH at work. (a) shows the mean and variance functions, as well as one realized dataset. (b) contrasts the difference in the distribution of the true wavelet coefficients at two different scales - one coarse and one fine. (c) demonstrates the shrinkage properties of ASH for the two scales of interest: the coefficients at the fine scale are substantially shrunk, but barely so for the coarse scale. (d) shows the shrinkage effect of ASH on the fine scale wavelet coefficients - wavelet coefficients are shrunk adaptively based on their precision. (e) plots the estimated mean functions from SMASH and TI-thresh against the true mean function; we see that TI-thresh has noticeable artifacts.}
    \label{fig:simple_eg}
\end{figure}
